Twisted graviton spectra of $AdS_4\times S^7$ and $AdS_7\times S^4$

### 2023-05-22 graviton spectra/content/index.tex
merge
almost done with index

%\documentclass[11pt]{amsart}
%
%%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}
%
%\begin{document}

@@

We begin by giving a definition of supergravity states suited to our context. The definition is meant to codify the following situation. Suppose we have a theory of gravity defined on a background of the form $AdS_{d+1} \times S^{d^\prime}$ where the conformal boundary of $AdS_{d+1}$ is a $d$ manifold $M$. We can compactify the theory, retaining all the Kaluza-Klein harmonics, to get a theory on $AdS_{d+1}$. A supergravity state is traditionally defined to be a solution to linearized equations of motion in this compactified theory with a given boundary value on $M^{d}$ \cite{WittenAdS}. Often, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values. Moreover, one may think of such boundary values as arising from modifications of a vacuum boundary condition at a point.

For twists of supergravity, we procedurally implement this as follows. First, we wish to describe a model for sphere compactification on twisted $AdS$ backgrounds. As we saw in the last section, our proposal for twists of backgrounds of the form $AdS_{d+1}\times S^{d^\prime}$ involve placing certain local $L_\infty$-algebras on certain manifolds of the form $X = \operatorname{Tot }(V\to Z)\setminus 0(Z)$. Note that $Z$ can be written as a sphere bundle over $\R_{>0}\times Z$ - the sphere compactification of our theory on $X$ is given by the pushforward to $\R_{>0}\times Z$. Such sphere compactifications can be described using a method for computing pushforwards of modules for Lie algebroids associated to foliations \cite[Sec. 4.2]{KormanThesis}, \cite{KamberTondeur}.

The compactified theory will admit a natural boundary condition at $\{\infty\}\times Z\subset \R_{>0}\times Z$, given by certain local $L_\infty$-algebras $\mc L$. In fact, the presence of extra differentials involving bracketing with the flux sourced by branes wrapping $Z$ will induce an interesting shifted-Poisosn structure on $\mc L$. Given a local $L_\infty$-algebra $\mc L$ underlying a perturbative classical field theory, the Chevalley-Eilenberg cochains $\clie^\bullet (\mc L)$ carry the structure of a $\mb{P}_0$-factorization algebra \cite{CG1}, \cite{CG2}. Associated to a factorization algebra, we can define a space of local operators, which is the costalk at a point of the underlying cosheaf. The sought-after spaces of supergravity states will be a space of local operators associated to $\clie^\bullet (\mc L)$.

@@

%The phase space is equipped with a natural symplectic form given by
%\[
%\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
%\]
%There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bullet}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
%The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$
\subsection{States on twisted $AdS_4\times S^7$}\label{s:ads4states}
Following the above prescription, we consider the $S^7$ bundle 
\[
\begin{tikzcd}
S^7 \ar[r] & \operatorname{Tot} (K^{1/4}_\C\otimes \C^4 \to \R\times \C) \setminus 0(\R\times \C) \ar[d, "p"] \\ & \R_{>0}\times \R\times \C
\end{tikzcd}
\]
We wish to describe the free limit of the pushforward $p_* \mc E^N_{AdS_4\times S^7}$ as a sheaf of cochain complexes on $\R_{>0}\times \R\times \C$.

\begin{prop}\label{prop:pushads4}
The pushforward is given by the sheaf of complexes $\Omega^\bullet_{\R_{>0}\times \R} \otimes \Omega^{0,\bullet}_{\C} (\mc V^N_\C)$ on $\R_{>0}\times \R\times \C$, where $\mc V^N_\C$ is the following dg-vector bundle on $\C$:

\begin{equation}
  \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
H^\bullet (\C^{4}\setminus 0, \T) \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & H^\bullet (\C^{4}\setminus 0) \otimes \mc O \\
H^\bullet (\C^{4}\setminus 0)  \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
H^\bullet (\C^{4}\setminus 0)\otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & H^\bullet (\C^{4}\setminus 0) \otimes \Omega^1 \\ & H^\bullet (\C^{4}\setminus 0, \Omega^1)  \otimes \mc O
\end{tikzcd}
\end{equation}

where the differentials are as follows:
\begin{itemize}
\item The differentials $\del_\Omega^Z$ and $\del_\Omega^W$ are the divergence operators along the base and fiber respectively.
\item The differentials $\del_Z$ and $\del_W$ are components of the holomorphic deRham differentials along the base and fiber respectively.
\item  Internal to each summand is a differential given by bracketing with the flux $NF_{M2}$. 
\end{itemize}
\end{prop}

@@

The flux $NF_{M2}$ of lemma \ref{lem:m2flux} is represented by the section $N (w_1\cdots w_4)^{-1}\del_z \in H^3 (\C^4\setminus 0)\otimes \T$ and acts on each summand by Lie derivative along $z$ and multiplying by $(w_1\cdots w_4)^{-1}$

\begin{proof}
To compute the pushforward of the kind of local $L_\infty$-algebra associated to a holomorphic-topological field theory along a map of THF manifolds, we can use a result of \cite[Sec. 4.2]{KormanThesis}, \cite{KamberTondeur} for describing direct images of Lie algebroid modules along maps of Lie algebroids. Schematically, if we have a proper submersion $p : X\to Z$ of THF manifolds, and a sheaf of complexes $\mc E$ on $X$ which resolves sections of some bundle flat along the leaves of the foliation on $X$, then the pushforward $p_*\mc E$ has a model as a partially flat bundle on $Z$. The fiber of this partially flat bundle on $Z$ is the THF cohomology of the fiber of $p$, with respect to the induced foliation on the fiber, with coefficients in the pullback of the bundle to the fiber. In the case of a holomorphic submersion, this recovers the usual construction of the Gauss-Manin connection for instance.

In our case, the pushforward $p_* \mc E_{AdS_4\times S^7}$ is a complex of $\Omega^\bullet_{\R_{>0}} \otimes \Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C$- modules given by

\begin{equation}
  \label{eqn:ads4ss} 
  \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
H^\bullet_{\mr{THF}}(S^7, \T) \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & H^\bullet_{\mr{THF}} (S^7) \otimes \mc O \\
H^\bullet_{\mr{THF}} (S^7)  \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
H^\bullet_{\mr{THF}} (S^7)\otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & H^\bullet_{\mr{THF}} (S^7) \otimes \Omega^1
 \\ & H^\bullet_{\mr{THF}} (S^7, \Omega^1)  \otimes \mc O
 \end{tikzcd}
\end{equation}

@@

\parsec{}
Continuing, we wish to understand a natural boundary condition we can place on the fields at $\{\infty\} \times\R\times \C\subset \R_{>0} \times \R\times \C$. Such a boundary condition is specified by a Lagrangian in the phase space. The restriction $(p_* \mc E^N_{AdS_4\times S^7})|_{\{\infty\}\times \C}$ describes the phase space and is easily seen to be $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc V^N_{\C})$. We wish to describe a shifted Lagrangian therein.

We begin by rewriting the phase space in the following form. Note that there is a higher residue pairing 
\[H^0(\C^4\setminus 0) \otimes H^3(\C^4\setminus 0) \to \C;\]
together with the natural pairings between $T, \Omega^1$ and the integration pairing along $\R\times \C_z$, this equips $\Omega^\bullet_\R\otimes \Omega^{0,\bullet}_{\C} (\mc V^N_{\C})$ with a local even-shifted symplectic structure.

Together with this shifted symplectic structure, we can identify the phase space with a twisted cotangent bundle
\[
 \Omega^\bullet_\R\otimes \Omega^{0,\bullet}_\C (\mc V^N_{\C}) = T^* _{\Pi} \left (\begin{tikzcd}[row sep = 1 ex]
 \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\T)\ar[ur, "\del^Z_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\Omega^1)\\ & \C[w_1,\ldots, w_4] \{\d w_a\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C   \end{tikzcd} \right) 
\]
For now, the subscript of $\Pi$ is just meant to indicate that the extra differential given by bracketing with the flux constitutes a deformation of the cotangent bundle.

Thus we see that a natural Lagrangian in the phase space is given by the sheaf of cochain complexes $\Omega^\bullet_\R\otimes\Omega^\bullet_\C (\mc L^N_{AdS_4\times S^7})$ where $\mc L^N_{AdS_4\times S^7}$ is the following dg-vector bundle

 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
       \ul{+} & \ul{-} \\ 
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \T\ar[ur, "\del^Z_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Omega^1
\\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O \end{tikzcd}
\end{equation}

\begin{rmk}
The extra term in the differential in fact equips $\Omega^\bullet_\R\otimes \Omega^\bullet_\C (\mc L^N_{AdS_4\times S^7} )$ with an interesting $N$ dependent odd-shifted Poisson structure. This will not play a significant role in the narrative of this thesis, but we flag it for later commentary nonetheless.
\end{rmk}

\begin{defn}\label{defn:ads4states}
 The \emph{space of supergravity states} on twisted $AdS_4\times S^7$ is given by the costalk at zero of the factorization algebra on $\R\times \C$ given by $\clie^\bullet \left (  \Pi \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C (\mc L^N_{AdS_4\times S^7}) \right )$
\end{defn}

\parsec{}
Let us explicate definition \ref{defn:ads4states} a bit. We wish to first understand the space of supergravity states as a cochain complex.

\begin{lem}\label{lem:ads4states}
The space of supergravity states on twisted $AdS_4\times S^7$ is the symmetric algebra $\Sym (\mc H_{AdS_4\times S^7})$ where $\mc H_{AdS_4\times S^7}$ is the cochain complex
 \begin{equation} 
 \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4]  \otimes \C[\del_z]\delta_{z=0} \\
\C[w_1,\ldots, w_4] \del_z  \otimes \C[\del_z]\delta_{z=0}\ar[ur, "\del^Z_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \d z \otimes \C[\del_z]\delta_{z=0} \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \C[\del_z]\delta_{z=0}
\end{tikzcd}
\end{equation}
\end{lem}

\begin{proof}
To compute the costalk at $0$ of a factorization algebra, we consider a nested sequence of open sets containing the origin and compute the limit of the value of the factorization algebra over this sequence. Consider open sets in $\R\times \C$ of the form $I\times D$ where $I\subset \R$ is an interval and $D\subset \C$ is a disc. The sections of the sheaf of cochain complexes $\Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C(\mc L^N_{AdS_4\times S^7} ) $ over this open set is given by \begin{equation}
\begin{tikzcd}[row sep = 1 ex]
    \ul{+} & \ul{-} \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}(D)\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O(D) \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \Gamma (D, \T)\ar[ur, "\del^Z_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}(D)\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Gamma (D, \Omega^1) \\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O(D)
\end{tikzcd}
\end{equation}

@@

\begin{equation}
 \clie^\bullet \left (\begin{tikzcd}[row sep = 1 ex]
        \ul{-} & \ul{+} \\ 
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \C[\![z]\!] \ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \C[\![z]\!] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \C[\![z]\!]\del_z\ar[ur, "\del^Z_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \C[\![z]\!]\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \C[\![z]\!]\d z \\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \C[\![z]\!]
\end{tikzcd} \right )
\end{equation}

The definition of the Chevalley-Eilenberg complex above involves the continuous linear dual of a chain complex of topological vector spaces. The duals of each of the tensor factors are as follows:

@@

Thus, we see that $\mc H_{AdS_4\times S^7}$ is indeed as claimed.
\end{proof}

\parsec{}
We proceed to computing a local character for the factorization algebra defined in \ref{defn:ads4states}; thanks to lemma \ref{lem:ads4states} we can compute this as a character of $\Sym(\mc H_{AdS_4\times S^7})$.

We first observe the following action of $\mf{sl}(4)\oplus \mf {sl}(2)$ on $\mc H_{AdS_4\times S^7}$. The $\mf{sl}(4)$ summand acts on the tensor factor $\C[w_1,w_2,w_3,w_4]$ in the obvious way - it's the symmetric algebra on the fundamental representation. The $\mf{sl}(2)$ summand acts by bracketing with the vector fields 
\[
\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right).
\]

@@

The weights of $\mc H_{AdS_4\times S^7}$ with respect to the generators of this Cartan subalgebra are entirely determined by the weights of the holomorphic coordinates $z, w_a, a= 1, \cdots, 4$, which we summarize in table \ref{tbl:sugraM2}

@@

\begin{lem}
The space of supergravity states on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7\times S^4} )$ where $\mc H_{AdS_7\times S^4}$ is given by the cochain complex

>>>>

\documentclass[../main.tex]{subfiles}

\begin{document}

@@

We begin by giving a definition of supergravity states suited to our context. 
The definition is meant to codify the following situation. 
Suppose we have a bulk gravitational theory defined on a background of the form $AdS_{d+1} \times S^{d^\prime}$ where the conformal boundary of $AdS_{d+1}$ is a $d$-dimensional manifold $M$. 
We can compactify the theory, retaining all the Kaluza-Klein harmonics, to get a theory on $AdS_{d+1}$. 
A gravitational state is traditionally defined to be a solution to linearized equations of motion in this compactified theory with a given boundary value on $M^{d}$ \cite{WittenAdS}. Often, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values. Moreover, one may think of such boundary values as arising from modifications of a vacuum boundary condition at a point.

For twists of supergravity, we procedurally implement this as follows. First, we wish to describe a model for sphere compactification on twisted $AdS$ backgrounds. 
As we saw in the last section, our proposal for describing twists backgrounds of the form $AdS_{d+1}\times S^{d^\prime}$ involve elliptic complexes defined on certain manifolds of the form 
\beqn
X = \operatorname{Tot }(V\to Z)\setminus 0(Z)
\eeqn
Note that $Z$ can be written as a sphere bundle over $\R_{>0}\times Z$ - the sphere compactification of our theory on $X$ is given by the pushforward to $\R_{>0}\times Z$. 
Such sphere compactifications can be described using a method for computing pushforwards of modules for Lie algebroids associated to foliations \cite[section 4.2]{KormanThesis}, \cite{KamberTondeur}.

The compactified theory will admit a natural boundary condition at $\{\infty\}\times Z\subset \R_{>0}\times Z$.
Such a boundary condition also admits a perturbative description in terms of some elliptic complex $\mc L$ on $Z$.
In fact, the presence of extra differentials involving bracketing with the flux sourced by branes wrapping $Z$ will induce an odd Poisson structure on $\mc L$.
Given an elliptic complex $\cL$ underlying a perturbative classical field theory, the algebra of observables $\cO(\cL)$ carries the structure of a $\mb{P}_0$-factorization algebra \cite{CG1}, \cite{CG2}. 
Associated to a factorization algebra, we can define a space of local operators, which is the costalk at a point of the underlying cosheaf.
The sought-after spaces of supergravity states will be a space of local operators associated to $\cO(\cL)$.

@@

%The phase space is equipped with a natural symplectic form given by
%\[
%\int_C \d z \oint_{S^2} \d w \, \alpha \wedge \alpha' .
%\]
%There is a natural Lagrangian inside of the phase space which consists of linear combinations of elements $\alpha(z) \otimes f(t,w)$ where $\alpha(z) \in \Omega^{0,\bullet}(C)$ and $f(t,w)$ is a smooth function on $\R \times \C - 0$ which extends to zero.
%The linearized equations of motion simply say that $\alpha$ is holomorphic, $f$ is independent of $t$ and depends holomorphically on $w$
\subsection{States on twisted $AdS_4\times S^7$}\label{s:ads4states}
We begin more generally with the input being a three-manifold $M$ equipped with a THF structure of codimension one.
As in \S \ref{s:??} the elliptic complex $\cA^\bu_M$ computes the THF cohomology of $M$.
We denote by $K$ the holomorphic canonical bundle of $M$ which has a local frame given by $\d z$.
The case of $AdS_4 \times S^7$ corresponds to taking $M = \R \times \C$, which we will do momentarily.

We will also fix a fourth-root $K^{1/4}$ of this bundle.
Following the above prescription, we consider the $S^7$ bundle 
\[
\begin{tikzcd}
S^7 \ar[r] & \operatorname{Tot} (K^{1/4} \otimes \C^4 \to M) \setminus 0(M) \ar[d, "p"] \\ & \R_{>0}\times M
\end{tikzcd}
\]
We wish to describe the free limit of the pushforward $p_* \mc E^N_{AdS_4}$ as a sheaf of cochain complexes on $\R_{>0}\times M$.

\begin{prop}\label{prop:pushads4}
The pushforward is given by the sheaf of complexes $\Omega^\bullet_{\R_{>0}} \otimes \cA^{\bullet}_{M} (\mc V^N)$ on $\R_{>0}\times M$, where $\mc V^N$ is the following complex of vector bundles on $M$:

\begin{equation}
  \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
H^\bullet (\C^{4}\setminus 0, \T) \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & H^\bullet (\C^{4}\setminus 0) \otimes \mc O \\
H^\bullet (\C^{4}\setminus 0)  \otimes \T\ar[ur, "\del^M_\Omega" description] \\
H^\bullet (\C^{4}\setminus 0)\otimes \mc{O}\ar[r, "\del_M" description]\ar[dr, "\del_W" description] & H^\bullet (\C^{4}\setminus 0) \otimes \Omega^1 \\ & H^\bullet (\C^{4}\setminus 0, \Omega^1)  \otimes \mc O
\end{tikzcd}
\end{equation}
where the differentials are as follows:
\begin{itemize}
\item The differentials $\del_\Omega^M$ and $\del_\Omega^W$ are the divergence operators along the base and fiber respectively.
\item The differentials $\del_M$ and $\del_W$ are components of the holomorphic de Rham differentials along the base and fiber respectively.
\item  Internal to each summand is a differential given by bracketing with the flux $NF_{M2}$, see equation \eqref{eqn:FM2}. 
\end{itemize}
\end{prop}

@@

The flux $NF_{M2}$ of lemma \ref{lem:m2flux} is represented by the section $N (w_1\cdots w_4)^{-1}\del_z \in H^3 (\C^4\setminus 0)\otimes \T$ and acts on each summand by Lie derivative along $z$ and multiplying by $(w_1\cdots w_4)^{-1}$.

\begin{proof}
To compute the pushforward of this sort of elliptic complex associated to a holomorphic-topological field theory along a map of THF manifolds, we can use a result of \cite[section 4.2]{KormanThesis}, \cite{KamberTondeur} for describing direct images of Lie algebroid modules along maps of Lie algebroids. Schematically, if we have a proper submersion $p : X\to Z$ of THF manifolds, and a sheaf of complexes $\mc E$ on $X$ which resolves sections of some bundle flat along the leaves of the foliation on $X$, then the pushforward $p_*\mc E$ has a model as a partially flat bundle on $Z$. The fiber of this partially flat bundle on $Z$ is the THF cohomology of the fiber of $p$, with respect to the induced foliation on the fiber, with coefficients in the pullback of the bundle to the fiber. In the case of a holomorphic submersion, this recovers the usual construction of the Gauss-Manin connection for instance.

In our case, the pushforward $p_* \mc E_{AdS_4}$ is a complex of $\Omega^\bullet_{\R_{>0}} \otimes \cA^\bu_M$- modules given by

\begin{equation}
  \label{eqn:ads4ss} 
  \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
H^\bullet_{\mr{THF}}(S^7, \T) \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & H^\bullet_{\mr{THF}} (S^7) \otimes \mc O \\
H^\bullet_{\mr{THF}} (S^7)  \otimes \T\ar[ur, "\del^X_\Omega" description] \\
H^\bullet_{\mr{THF}} (S^7)\otimes \mc{O}\ar[r, "\del_X" description]\ar[dr, "\del_W" description] & H^\bullet_{\mr{THF}} (S^7) \otimes \Omega^1
 \\ & H^\bullet_{\mr{THF}} (S^7, \Omega^1)  \otimes \mc O
 \end{tikzcd}
\end{equation}

@@

\parsec{}
We proceed to define a natural boundary condition of the twisted $AdS_4$-type theory at $\{\infty\} \times M \subset \R_{>0} \times M$. 
Such a boundary condition is specified by a Lagrangian in the phase space whose symplectic structure uses Serre duality on the THF manifold $M$ together with the higher residue pairing along the THF structure of the sphere $S^7$. 
The restriction $(p_* \mc E^N_{AdS_4})|_{\{\infty\}\times \C}$ describes the phase space and is easily seen to be $\cA_M^\bu (\mc V^N)$. We wish to describe a shifted Lagrangian therein.

We begin by rewriting the phase space in the following form. 
Using the holomorphic volume form, there is a higher residue pairing 
\[H^0(\C^4\setminus 0, \cO) \otimes H^3(\C^4\setminus 0, \cO) \to \C;\]
together with the natural pairings between $T, \Omega^1$ and the integration along $M$, this equips $\cA_M^\bu (\mc V^N)$ with a local even-shifted symplectic structure.

Via this symplectic structure, we can identify the phase space with a twisted cotangent bundle
\[
\cA_M^\bu (\mc V^N) = T^* _{\alpha} \left (\begin{tikzcd}[row sep = 1 ex]
 \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\T)\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C(\Omega^1)\\ & \C[w_1,\ldots, w_4] \{\d w_a\} \otimes \Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C   \end{tikzcd} \right) 
\]
For now, the subscript of $\alpha$ is just meant to indicate that the extra differential given by bracketing with the flux constitutes a deformation of the cotangent bundle.

Thus we see that a natural Lagrangian in the phase space is given by the sheaf of cochain complexes $\cA^\bu_M(\mc L^N_{AdS_4})$ where $\mc L^N_{AdS_4}$ is the following complex of vector bundles on $M$:

 \begin{equation}
 \begin{tikzcd}[row sep = 1 ex]
       \ul{+} & \ul{-} \\ 
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \T\ar[ur, "\del^M_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Omega^1
\\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O \end{tikzcd}
\end{equation}

We now specialize to the case $M = \R \times \C$.

\begin{defn}\label{defn:ads4states}
 The \emph{space of supergravity states} on twisted $AdS_4\times S^7$ is given by the costalk at zero of the factorization algebra on $\R\times \C$ given by 
 \beqn
 \cO\left(\Omega^\bullet_\R \otimes \Omega^{0,\bullet}_\C (\mc L^N_{AdS_4}) \right ) .
 \eeqn
\end{defn}

\parsec{}
We explicate definition \ref{defn:ads4states} and characterize the cochain complex underlying the space of supergravity states.

\begin{lem}\label{lem:ads4states}
The space of supergravity states on twisted $AdS_4\times S^7$ is the symmetric algebra $\Sym (\mc H_{AdS_4})$ where $\mc H_{AdS_4}$ is the cochain complex
 \begin{equation} 
 \begin{tikzcd}[row sep = 1 ex]
    \ul{-} & \ul{+} \\ 
\C[w_1,\ldots, w_4] \{\partial_{w_a}\} \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del^W_\Omega" description] & \C[w_1,\ldots, w_4]  \otimes \C[\del_z]\delta_{z=0} \\
\C[w_1,\ldots, w_4] \del_z  \otimes \C[\del_z]\delta_{z=0}\ar[ur, "\del^M_\Omega" description] \\
\C[w_1,\ldots, w_4] \otimes \C[\del_z]\delta_{z=0}\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & \C[w_1,\ldots, w_4] \d z \otimes \C[\del_z]\delta_{z=0} \\ & \C[w_1,\ldots, w_4] \{\d w_a\}  \otimes \C[\del_z]\delta_{z=0}
\end{tikzcd}
\end{equation}
\end{lem}

\begin{proof}
To characterize the costalk at $0 \in \R \times \C$ of a factorization algebra, we consider a nested sequence of open sets containing the origin and compute the limit of the value of the factorization algebra over this sequence. Consider open sets in $\R\times \C$ of the form $I\times D$ where $I\subset \R$ is an interval and $D\subset \C$ is a disc. The sections of the sheaf of cochain complexes $\Omega^\bullet _\R \otimes \Omega^{0,\bullet}_\C(\mc L^N_{AdS_4\times S^7} ) $ over this open set is given by \begin{equation}
\begin{tikzcd}[row sep = 1 ex]
    \ul{+} & \ul{-} \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \mc{O}(D)\ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \mc O(D) \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \Gamma (D, \T)\ar[ur, "\del^M_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \mc{O}(D)\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \Gamma (D, \Omega^1) \\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \mc O(D)
\end{tikzcd}
\end{equation}

@@

\begin{equation}
\cO\left (\begin{tikzcd}[row sep = 1 ex]
        \ul{+} & \ul{-} \\ 
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\partial_{w_a}\} \otimes \C[\![z]\!] \ar[r, "\del^W_\Omega" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]  \otimes \C[\![z]\!] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}]   \otimes \C[\![z]\!]\del_z\ar[ur, "\del^M_\Omega" description] \\
(w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \C[\![z]\!]\ar[r, "\del_Z" description]\ar[dr, "\del_W" description] & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \otimes \C[\![z]\!]\d z \\ & (w_1\cdots w_4)^{-1} \C[w_1^{-1},\ldots, w_4^{-1}] \{\d w_a\}  \otimes \C[\![z]\!]
\end{tikzcd} \right )
\end{equation}

The definition of algebraic functions $\cO(-)$ involves the continuous linear dual of a chain complex of topological vector spaces. 
The duals of each of the tensor factors are as follows:

@@

Thus, we see that $\mc H_{AdS_4}$ is indeed as claimed.
\end{proof}

\parsec{}
We proceed to computing a local character for the factorization algebra defined in \ref{defn:ads4states}; thanks to lemma \ref{lem:ads4states} we can compute this as a character of $\Sym(\mc H_{AdS_4})$.

We first observe the following action of $\mf{sl}(4)\oplus \mf {sl}(2)$ on $\mc H_{AdS_4}$. The $\mf{sl}(4)$ summand acts on the tensor factor $\C[w_1,w_2,w_3,w_4]$ in the obvious way - it's the symmetric algebra on the fundamental representation. The $\mf{sl}(2)$ summand acts by bracketing with the vector fields 
\[
\frac{\del}{\del z} ,\quad z \frac{\del}{\del z} - \frac14 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} , \quad z \left(z \frac{\del}{\del z} - \frac12 \sum_{a=1}^4 w_a \frac{\del}{\del w_a} \right).
\]

@@

The weights of $\mc H_{AdS_4}$ with respect to the generators of this Cartan subalgebra are entirely determined by the weights of the holomorphic coordinates $z, w_a, a= 1, \cdots, 4$, which we summarize in table \ref{tbl:sugraM2}

@@

\begin{lem}
The space of supergravity states on twisted $AdS_7\times S^4$ is the symmetric algebra $\Sym (\mc H_{AdS_7} )$ where $\mc H_{AdS_7}$ is given by the cochain complex
